Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-07-27 Paper/main.tex
Edit Posili figure
edit

\begin{figure}[H]
    \caption{ }
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_liqtotal.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{oos_fit_categorical.tiff}
     \end{subfigure}

        \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{oos_fit_duracion.tiff}
        \end{center}
        {\footnotesize \textit{Notes: }}
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

@@

>>>>

@@

\begin{figure}[H]
    \caption{Out of sample fit for duration predictions}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of duration predictions and outcomes }
        {\footnotesize \textit{RScript: }  \texttt{covariate_plots.R}}
\end{figure}

\begin{figure}[H]
    \caption{Out of sample fit for compensation predictions}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes.}
        {\footnotesize \textit{RScript: }  \texttt{covariate_plots.R}}
\end{figure}
